Towards Transparency and Open Science

### 2023-01-21 manuscript.Rmd
fix broken hyperrefs

---
title: "Towards Transparency and Open Science"
subtitle: "A Principled Perspective on Computational Reproducibility and Preregistration"
output:
  bookdown::pdf_document2:
    latex_engine: "xelatex"
    toc: true
    number_sections: false
header-includes: |
  \usepackage{libertine}
  \usepackage{pdfpages}

  \usepackage{titling}
  \let\paragraph\oldparagraph
  \let\subparagraph\oldsubparagraph
  \usepackage[sc, compact, raggedright]{titlesec}

  \pretitle{
     \begin{minipage}{\textwidth}
     \includepdf[offset=5mm 0mm]{cover.pdf}
     \end{minipage}
     \newpage
     \clearpage%
     \thispagestyle{empty}%
     \addtocounter{page}{-2}%
     \null%
     \clearpage
     \begin{center}\LARGE}
  \posttitle{\end{center}}

>>>>

---
title: "Towards Transparency and Open Science"
subtitle: "A Principled Perspective on Computational Reproducibility and Preregistration"
output:
  bookdown::pdf_document2:
    latex_engine: "xelatex"
    toc: true
    number_sections: false
    keep_tex:  true
header-includes: |
  \usepackage{libertine}
  \usepackage{pdfpages}

  % below works well with hyperref, but spacing is standard (to large)
  %\usepackage{sectsty}
  %\sectionfont{\Large\normalfont\scshape\raggedright}
  %\subsectionfont{\large\normalfont\scshape\raggedright}

    % titlesec does not play nice with RMarkdown, so hack:
  \let\paragraph\oldparagraph
  \let\subparagraph\oldsubparagraph
  \usepackage[sc, compact, raggedright]{titlesec}
  % titlesec does not play nice with hyperref, so hack:
  \newcommand{\sectionbreak}{\phantomsection}
  \newcommand{\subsectionbreak}{\phantomsection}

  \usepackage{titling}
  \pretitle{
     \begin{minipage}{\textwidth}
     \includepdf[offset=5mm 0mm]{cover.pdf}
     \end{minipage}
     \newpage
     \clearpage%
     \thispagestyle{empty}%
     \addtocounter{page}{-2}%
     \null%
     \clearpage
     \begin{center}\LARGE}
  \posttitle{\end{center}}
